---
title: "Breast Cancer Proteomes"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("ggplot2")
library("gridExtra")
```

First looking at the cancer samples data:

```{r}
samples <- as.data.frame(read.csv("./data/clinical_data_breast_cancer.csv", header = TRUE))
```

Looking some of the summary data

```{r}
dim(samples)
summary(samples)
```

There are 105 samples with 30 different features.
* **Complete.TCGA.ID**: The ID of the sample 
* **Gender**:
* **Age.at.Initial.Pathologic.Diagnosis**:
* **ER.Status**: Estrogen Receptor Status
* **PR.Status**: Progesterone Receptor Status
* **HER2.Final.Status**: Human Epidermal Growth Factor-2
* **Tumor**: Factors of the size of the Tumor (T1, T2, T3, T4)
* **Tumor..T1.Coded**: Coded for just T1 tumors
* **Node**: Factor of how far the cancer has spread to nearby nodes with N0 indicating no spread. (N0, N1, N2, N4)
* **Node.Coded**: Negative indicates N0 (no spread), Positive indicates N1-N3.
* **Metastasis**: Factor indicating if cancer has spread to other parts of the body. M0 indicates no distant metastatis, M1 indicates Distant metastasis
* **Metastasis.Coded**: Negative indicates M0, Positive indicates M1
* **AJCC.Stage**: Factors of the stage of the concers. This is determined by combining the T, N, and M categories.
* **Converted.Stage**
* **Survival.Data.Form**: 
* **Vital.Status**: 
* **Days.to.Date.of.Last.Contact**
* **Days.to.date.of.Death**
* **OS.event**
* **S.Time**
* **PAM50.mRNA**
* **SigClust.Unsupervised.mRNA**
* **SigClust.Intrinsic.mRNA**
* **miRNA.Clusters**
* **methylation.Clusters**
* **RPPA.Clusters**
* **CN.Clusters**
* **Integrated.Clusters..with.PAM50.**
* **Integrated.Clusters..no.exp.**
* **Integrated.Clusters..unsup.exp.**

```{r Age}
ggplot(samples, aes(x = Age.at.Initial.Pathologic.Diagnosis)) +
  geom_histogram(colour = "darkgreen", fill = "white", binwidth = 3)
```

```{r Status}
plot_ER <- ggplot(samples, aes(x = ER.Status)) +
  geom_bar()
plot_PR <- ggplot(samples, aes(x = PR.Status)) +
  geom_bar()

grid.arrange(plot_ER, plot_PR, ncol=2)
```

```{r Types}
plot_Tumor <- ggplot(samples, aes(x = Tumor)) +
  geom_bar()
plot_Node <- ggplot(samples, aes(x = Node)) +
  geom_bar()
plot_Metastasis <- ggplot(samples, aes(x = Metastasis)) +
  geom_bar()

grid.arrange(plot_Tumor, plot_Node, plot_Metastasis, ncol=3)
```






