---
title: "Breast Cancer Proteomes"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First looking at the cancer samples data:

```{r}
samples <- as.data.frame(read.csv("./data/clinical_data_breast_cancer.csv", header = TRUE))
```

Looking some of the summary data

```{r}
dim(samples)
summary(samples)
```

There are 105 samples with 30 different features.
* Complete.TCGA.ID: The ID of the sample
* Gender
* Age.at.Initial.Pathologic.Diagnosis
* ER.Status:
* PR.Status
* HER2.Final.Status
* Tumor
* Tumor..T1.Coded
* Node
* Node.Coded
* Metastasis
* Metastasis.Coded
* AJCC.Stage
* Converted.Stage
* Survival.Data.Form
* Vital.Status
* Days.to.Date.of.Last.Contact
* Days.to.date.of.Death
* OS.event
* OS.Time
* PAM50.mRNA
* SigClust.Unsupervised.mRNA
* SigClust.Intrinsic.mRNA
* miRNA.Clusters
* methylation.Clusters
* RPPA.Clusters
* CN.Clusters
* Integrated.Clusters..with.PAM50.
* Integrated.Clusters..no.exp.
* Integrated.Clusters..unsup.exp.







